---
title: "Vignette for corr_level1 Function"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{corr_level1}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  message = FALSE
)
```




# Introduction
This vignette demonstrates how to use the corr_level1 function to calculate and format correlation matrices with additional metrics like mean, standard deviation, and Cronbach's alpha.

Example

#Setup: Load The Package and Required Packages
The function requires the psych package to compute Cronbach’s alpha.

```{r}
library(mltable)
library(psych)  # For Cronbach's alpha calculation

# Load built-in dataset
data(teamstate)
```

# Basic Usage
## Define Variable Groups in var_list
Each entry represents a list of item of variables.

```{r}
var_list <- list( 
  var1 = 3,         # Single column (Gender item) 
  var2 = 4,         # Single column (Age item) 
  var3 = 5:14,      # Columns 5-14 (PosAffect items) 
  var4 = 15:24,     # Columns 15-24 (NegAffect items) 
  var5 = 25:28      # Columns 25-28 (PsySafety items) 
) 
```

## Generate Correlation Matrix
```{r}
result <- corr_level1(
  data = teamstate,
  var_list = var_list,
  var_labels = c("Gender", "Age", "Positive Affect", 
                "Negative Affect", "Psychological Safety"),
  digits = 2
)
```

# Key Features
## 1. Additional Metrics
Means and SDs automatically calculated

Cronbach's alpha for multi-item composites

## 2. Formatting Options
Control decimal places with digits

Choose matrix triangle with triangle

Toggle significance stars with show_significance

## 3. Missing Data Handling
Default pairwise deletion (use = "pairwise.complete.obs")

# Advanced Customization
## Show upper triangle with 2 decimal places and Keep leading zeros

```{r}
corr_level1( 
  teamstate, var_list, 
  triangle = "upper", 
  digits = 2, 
  lead.decimal = TRUE  # Keep leading zeros (e.g., 0.123) 
) 
```

## Suppress Metrics
```{r}
corr_level1( 
  teamstate, var_list, 
  mean = FALSE, 
  alpha = FALSE 
) # Exclude mean and Cronbach's alpha 
```

## Exporting Results
Save the formatted matrix as a CSV file.

```{r}
write.csv(result, "correlation_table.csv", row.names = TRUE) 
```

# Important Notes
All variables in var_list must be numeric.

Cronbach's alpha requires ≥2 items.

Use column names instead of indices for reliability.

Check variable labels match var_list order.

For complete documentation: ?corr_level1
