---
title: "Vignette for corr_level2 Function"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{corr_level2}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  message = FALSE,
  options(rmarkdown.html_vignette.check_title = FALSE)
)
```


# Introduction
This vignette demonstrates how to use corr_level2 to calculate group-level correlations with additional multilevel metrics including rwg.j (within-group agreement) and reliability estimates.

# Setup
```{r}
library(mltable)
library(multilevel)  # For rwg.j calculation
library(psych)       # For Cronbach's alpha

# Load built-in dataset
file_path <- system.file("extdata", "teamstate.csv", package = "mltable")
teamstate <- read.csv(file_path)
```

# Basic Usage
## Define Group Structure

```{r}
var_list2 <- list(
   var1 = 5:14,    # Team positive affect
   var2 = 15:24,   # Team negative affect
   var3 = 25:28    # Team psychological safety
  )
```

## Generate Group-Level Correlations
```{r}
result <- corr_level2(data = teamstate,
                      var_list = var_list2,
                      groupid = "Team",  # Group identifier column
                      var_labels = c("Team PA", "Team NA", "Team PS"),
                      rwg_scale = 7,     # 7-point response scale
)
```

# Key Features
##1. Multilevel Metrics
rwg.j: Within-group agreement (mean as default)

Reliability calculated by Level 1 items: Cronbach's alpha

Aggregated means/SDs

##2. Specialized Handling
Automatic data aggregation by group.

Missing data handling.

Response scale specification for rwg.j (e.g., 5-Likert scale as default, you may change to 7 of your survey use 7-Likert scale).

##3. Presentation Options
Flexible triangle formatting

Significance indicators

Decimal control

# Advanced Customization
## Median rwg.j with 7-point Scale
```{r}
corr_level2(
  teamstate,
  var_list2,
  groupid = "Team",
  rwg_method = "median",
  rwg_scale = 7,
  lead.decimal = FALSE
)
```

## Minimal Output
```{r}
corr_level2(
  teamstate,
  var_list2,
  groupid = "Team",
  mean = FALSE,
  alpha = FALSE,
  rwg = FALSE
)
```

## Export Results
Save the formatted matrix as a CSV file.
```{r}
write.csv(result, "team_level_correlations.csv", row.names = TRUE)
```

# Important Notes
Requires valid group identifier column.

rwg.j requires ≥2 items per construct.

Response scale must match actual item range.

All constructs must be numeric.

Install multilevel package first if missing.

For complete documentation: ?corr_level2
